PANCHANGE_data_preprocessing

### 2020-10-02 PANCHANGE_data_preprocessing2020-07-15.Rmd

dem.raw.id <- dem.raw.id %>%
  mutate(
    Ethnicity = 
      recode_factor(Ethnicity_unc,
        "White" = "European",
        "Mixed" = "Mixed or multiple ethnic origins",
        "Asian or Asian British" = "Asian or Asian British",
        "Black or Black British" = "African or African British",
        "Arab" = "Arab",
        "Other ethnic group:" = "Other ethnic group"
      )
  ) %>%
  rename(
    Ethnicity_numeric = Ethnicity_unc_numeric
  )
}
```

@@

dem.raw.id <- dem.raw.id %>%
  mutate(
    Ethnicity = 
      recode_factor(Ethnicity_unc,
        "White, white European or Caucasian" = "European",
        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
        "Black or Black British" = "African or African British",
        "Arab" = "Arab",
        "Other ethnic group (please specify)" = "Other ethnic group"
      )
  ) %>%
  rename(
    Ethnicity_numeric = Ethnicity_unc_numeric
  )
}
```

@@

dem.raw.id <- dem.raw.id %>%
  mutate(
    Ethnicity = 
      recode_factor(Ethnicity_unc,
        "White, white European or Caucasian" = "European",
        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
        "Black or Black British" = "African or African British",
        "Arab" = "Arab",
        "Other ethnic group (please specify)" = "Other ethnic group"
      )
  ) %>%
  mutate(
    Ethnicity_numeric = 
      recode(Ethnicity,
        "European" = 1,
        "Mixed or multiple ethnic origins" = 2,
        "Asian or Asian British" = 3,
        "African or African British" = 4,
        "Arab" = 5,
        "Other ethnic group" = 6
      )
  )
}
```

>>>>

dem.raw.id <- dem.raw.id %>%
  mutate(
    Ethnicity = 
      recode_factor(Ethnicity_unc,
        "White" = "White",
        "Mixed" = "Mixed or multiple ethnic origins",
        "Asian or Asian British" = "Asian or Asian British",
        "Black or Black British" = "Black or Black British",
        "Arab" = "Arab",
        "Other ethnic group:" = "Other ethnic group"
      )
  ) %>%
  rename(
    Ethnicity_numeric = Ethnicity_unc_numeric
  )
}
```

@@

dem.raw.id <- dem.raw.id %>%
  mutate(
    Ethnicity = 
      recode_factor(Ethnicity_unc,
        "White, white European or Caucasian" = "White",
        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
        "Black or Black British" = "Black or Black British",
        "Arab" = "Arab",
        "Other ethnic group (please specify)" = "Other ethnic group"
      )
  ) %>%
  rename(
    Ethnicity_numeric = Ethnicity_unc_numeric
  )
}
```

@@

dem.raw.id <- dem.raw.id %>%
  mutate(
    Ethnicity = 
      recode_factor(Ethnicity_unc,
        "White, white European or Caucasian" = "White",
        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
        "Black or Black British" = "Black or Black British",
        "Arab" = "Arab",
        "Other ethnic group (please specify)" = "Other ethnic group"
      )
  ) %>%
  mutate(
    Ethnicity_numeric = 
      recode(Ethnicity,
        "White" = 1,
        "Mixed or multiple ethnic origins" = 2,
        "Asian or Asian British" = 3,
        "Black or Black British" = 4,
        "Arab" = 5,
        "Other ethnic group" = 6
      )
  )
}
```
